# RMarkdown Template

## Setup

For more information about how to set up set up BigQuery usage in R see [this page](https://github.com/googlegenomics/getting-started-bigquery/blob/master/RMarkdown/literate-programming-demo.md#data-visualization) from google genomics.

#### Set project details

```{r eval=FALSE}
######################[ CHANGE ME ]##################################
# This codelab assumes that the current working directory is where the Rmd file resides.
setwd("/Users/gmcinnes/GitHub/mvp_aaa_codelabs/qc")

# Set the Google Cloud Platform project id under which these queries will run.
project <- "gbsc-gcp-project-mvp"
#####################################################################
```

#### Set up query function
```{r eval=TRUE, warning=FALSE}
# Set up for BigQuery access.
source("./rHelpers/setup.R")
```

#### Define tables to be used in queries 
```{r}
tableReplacement <- list("_THE_TABLE_"="gbsc-gcp-project-mvp:va_aaa_pilot_data.5_genome_test_gvcfs_2",
                         "_THE_EXPANDED_TABLE_"="gbsc-gcp-project-mvp:va_aaa_pilot_data.5_genome_test_vcfs_2",
                         "_REF_TABLE_"="gbsc-gcp-project-mvp:qc_tables.5_genomes_ref_calls_brca1",
                         "_VARIANT_TABLE_"="gbsc-gcp-project-mvp:qc_tables.5_genomes_variants_brca1")

sampleData <- read.csv("./data/patient_info.csv")
sampleInfo <- select(sampleData, call_call_set_name=Catalog.ID, gender=Gender)

constraints <- list("#_WHERE_"="WHERE 
                    reference_name = 'chr17'
                    AND start BETWEEN 41196311
                    AND 41277499")

googleRepository = "https://raw.githubusercontent.com/googlegenomics/codelabs/master/R/PlatinumGenomes-QC/sql/"
```

## Executing queries

Queries can be imported from a local file, from the internet, or by pasting the query into the rmarkdown file.  

In this example we'll look at all the variants found within brca1 for our sample cohort.
```{r message=FALSE, warning=FALSE, comment=NA}
query <- "https://raw.githubusercontent.com/googlegenomics/getting-started-bigquery/master/sql/sample-variant-counts-for-brca1.sql"
result <- DisplayAndDispatchQuery(query,
                                  project=project,
                                  replacements=tableReplacement)
```
Number of rows returned by this query: `r nrow(result)`.

Displaying the first few results:
```{r echo=FALSE, message=FALSE, warning=FALSE, comment=NA, results="asis"}
print(xtable(head(result)), type="html", include.rownames=F)
```

Plot it:
```{r example, fig.align="center", fig.width=10}
ggplot(result, aes(x=call_set_name, y=variant_count)) +
  geom_bar(stat="identity") + coord_flip() +
  ggtitle("Count of Variants Per Sample")
```

## Generate Markdown File
Execute the the following commands to create the markdown file.
```
require(knitr)

setwd("/YOUR/WORKING/DIRECTORY")
knit("./RMarkdown_Template.Rmd")
```
  